---
title: "<center>**ggstatsplot in R**</center>"
author: "<center>Wyclife Agumba Oluoch (wyclifeoluoch@gmail.com) </center>"
date: "<center>`r Sys.time()`</center>"
bibliography: 
  - bib/packages.bib
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: darkly
    #highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, cache = TRUE)
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
packages <- c("base",
              'knitr',
              'rmarkdown',
              'prettydoc',
              'ggstatsplot',
              'ggplot2')
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# Project Background

In this tutorial, I am showing the usage of `ggstatsplot` for annotating statistical values on ggplot graphics.

## ggbetweenstats

```{r}
ggbetweenstats(data = movies_long, x = mpaa, y = rating)
```

The plot can be improved to provide more information as follows:

```{r}
ggbetweenstats(data = movies_long, x = mpaa, y = rating,
               type = 'np', pairwise.display = 'ns')
```

or

```{r}
ggbetweenstats(data = movies_long, 
               x = mpaa, 
               y = rating,
               type = 'r', 
               pairwise.comparisons = FALSE,
               outlier.tagging = TRUE,
               outlier.label = title)
```

## ggwithinstats

The same can also be done for the `ggwithinstats` as follows:

```{r}
ggwithinstats(data = WRS2::WineTasting, Wine, Taste)
```

## gghistostats

```{r}
gghistostats(data = movies_long, x = budget, test.value = 30)
```

## ggdotplotstats

```{r}
ggdotplotstats(movies_long,
               budget, genre, test.value = 30)
```

## ggscatterstats

```{r}
ggscatterstats(movies_long, budget, rating,
               type = 'r',
               label.var = title, 
               label.expression = budget > 150 & rating > 7.5)
```

## ggcorrmat

```{r}
ggcorrmat(dplyr::starwars, type = 'bayes', output = 'data.frame')

```

## ggpiestats

```{r}
ggpiestats(
  data         = mtcars,
  x            = am,
  y            = cyl,
  package      = "wesanderson",
  palette      = "Royal1",
  title        = "Dataset: Motor Trend Car Road Tests", ## title for the plot
  legend.title = "Transmission", ## title for the legend
  caption      = "Source: 1974 Motor Trend US magazine"
)

```

## ggbarstats

```{r}
ggbarstats(
  data             = movies_long,
  x                = mpaa,
  y                = genre,
  title            = "MPAA Ratings by Genre",
  xlab             = "movie genre",
  legend.title     = "MPAA rating",
  ggtheme          = hrbrthemes::theme_ipsum_pub(),
  ggplot.component = list(ggplot2::scale_x_discrete(guide = ggplot2::guide_axis(n.dodge = 2))),
  palette          = "Set2"
)
```

## ggcoefstats
This is plotting

```{r}
mod <- lm(rating~mpaa, data = movies_long)
ggcoefstats(mod)
```

## grouped_ggpiestats

```{r}
grouped_ggpiestats(mtcars, x = cyl, grouping.var = am)
```

## ggbetweenstats customized

```{r}
ggbetweenstats(movies_long, 
               mpaa, rating, 
              ggtheme = hrbrthemes::theme_ipsum_tw(),
              palettete = "Darjeeling2")
```

That seemed a nice way to work around visualizing statistics using the ggplot graphics.

# References